---
output:
  word_document: default
  html_document: default
---
Advanced classfication to evaluate credit risk.

Liang Hu

Load libraries.
```{r}
library(caret)
library(RWeka)
library(e1071)
library(DMwR)
library(randomForest)
library(ggplot2)
```

Read data.
```{r}
setwd(getwd())
credit <- read.csv("credit-g.csv")
```

Use SMOTE to improve minority class prediction.
```{r}
set.seed(1991)
credit_smote <- SMOTE(class~., data=credit)                         
table(credit_smote$class) 
```

Use 10-fold cross-validation to evaluate error.
```{r}
ctrl_cv10 <- trainControl(method='cv', number=10, savePredictions=T,
                          classProbs=T)
```

Build the random forest model.
```{r}
model_RF <- train(class~., data=credit_smote, method='rf', trControl=ctrl_cv10)
model_RF
prediction_RF <- predict(model_RF, credit_smote)
confusionMatrix(prediction_RF, credit_smote$class)
plot(model_RF)
```

Build the SVM model using linear kernel.
```{r}
model_SVM1 <- train(class~., data=credit_smote, method='svmLinear2', trControl=ctrl_cv10)
model_SVM1
prediction_SVM1 <- predict(model_SVM1, credit_smote)
confusionMatrix(prediction_SVM1, credit_smote$class)
```

Tune the parameters of the SVM model using linear kernel.
```{r}
model_SVM2 <- train(class~., data=credit_smote, method='svmLinear2', trControl=ctrl_cv10, tuneGrid=expand.grid(cost=0.1*c(1:10)))
model_SVM2
prediction_SVM2 <- predict(model_SVM2, credit_smote)
confusionMatrix(prediction_SVM2, credit_smote$class)
plot(model_SVM2)
```

Build the SVM model using polynomial kernel.
```{r}
model_SVM3 <- train(class~., data=credit_smote, method='svmPoly', trControl=ctrl_cv10)
model_SVM3
prediction_SVM3 <- predict(model_SVM3, credit_smote)
confusionMatrix(prediction_SVM3, credit_smote$class)
```

Tune the parameters of the SVM model using polynomial kernel.
```{r}
svmGrid <- expand.grid(degree=(1:10),
                       scale=0.1,
                       C=c(0.25,0.5,1))
model_SVM4 <- train(class~., data=credit_smote, method='svmPoly', trControl=ctrl_cv10, tuneGrid=svmGrid)
model_SVM4
prediction_SVM4 <- predict(model_SVM4, credit_smote)
confusionMatrix(prediction_SVM4, credit_smote$class)
ggplot(model_SVM4)
```

Build the SVM model using RBF kernel.
```{r}
model_SVM5 <- train(class~., data=credit_smote, method='svmRadial', trControl=ctrl_cv10)
model_SVM5
prediction_SVM5 <- predict(model_SVM5, credit_smote)
confusionMatrix(prediction_SVM5, credit_smote$class)
plot(model_SVM5)
```

Tune parameters of the SVM model using RBF kernel.
```{r}
model_SVM6 <- train(class~., data=credit_smote, method='svmRadial', trControl=ctrl_cv10, tuneGrid=expand.grid(sigma=0.01*seq(1,2,0.1),
                                         C=c(0.25,0.5,1)))
model_SVM6
prediction_SVM6 <- predict(model_SVM6, credit_smote)
confusionMatrix(prediction_SVM6, credit_smote$class)
plot(model_SVM6)
```



