---
output:
  word_document: default
  html_document: default
---
Liang Hu

load libraries
```{r}
library(caret)
library(RWeka)
library(e1071)
library(DMwR)
```

read data
```{r}
setwd(getwd())
credit <- read.csv("credit-g.csv")
```

use cross-validation to evaluate error
```{r}
ctrl_cv10 <- trainControl(method='cv', number=10, savePredictions = T,
                          classProbs = T)
```

build a decision tree model without input engineering as reference
```{r}
set.seed(1992)
model_DT <- train(class~., data=credit, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT
prediction_DT = predict(model_DT, credit)
confusionMatrix(prediction_DT, credit$class)
```

select attributes to improve model
```{r}
filterCtrl <- sbfControl(functions = treebagSBF, method = "repeatedcv",
                         repeats = 5)
sbf(x=credit, y=credit$class, sbfControl = filterCtrl)
```

variable importance
```{r}
DT_Imp <- varImp(model_DT, scale = FALSE)
DT_Imp
plot(DT_Imp)
```

the Univariate Filters select 4 variables;
"checking_status" is very important;
therefore choose 5 variables
```{r}
credit_select <- credit[, c('checking_status', 'duration', 'credit_amount', 'installment_commitment', 'age', 'class')]
```

build the decision tree model based on selected attributes
```{r}
model_DT_select <- train(class~., data=credit_select, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT_select
prediction_DT_select = predict(model_DT_select, credit_select)
confusionMatrix(prediction_DT_select, credit_select$class)
```

construct attributes to improve model
```{r}
credit_constr <- credit[, -ncol(credit)]
#whether a worker?
credit_constr$worker <- 'yes'
credit_constr$worker[credit_constr$employment=='unemployed'] <- 'no'
credit_constr$worker <- as.factor(credit_constr$worker)
#gender
credit_constr$gender <- ifelse(credit_constr$personal_status=="'female div/dep/mar'", 'female', 'male')
credit_constr$gender <- as.factor(credit_constr$gender)
#married?
credit_constr$married <- ifelse(credit_constr$personal_status=="'male single'", 'no', 'yes')
credit_constr$married <- as.factor(credit_constr$married)
credit_constr$class <- credit$class
```

build decision tree model based on old and new attributes
```{r}
model_DT_constr <- train(class~., data=credit_constr, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT_constr
prediction_DT_constr = predict(model_DT_constr, credit_constr)
confusionMatrix(prediction_DT_constr, credit_constr$class)
```

under-sampling to improve minority class prediction
```{r}
set.seed(1991)
credit_down <- downSample(x = credit[, -ncol(credit)],
                         y = credit$class)
table(credit_down$Class) 
```

build decision tree model based on under-sampling data
```{r}
model_DT_down <- train(Class~., data=credit_down, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT_down
prediction_DT_down = predict(model_DT_down, credit_down)
confusionMatrix(prediction_DT_down, credit_down$Class)
```

over-sampling to improve minority class prediction
```{r}
set.seed(1991)
credit_up <- upSample(x = credit[, -ncol(credit)],
                         y = credit$class)
table(credit_up$Class) 
```

build decision tree model based on over-sampling data
```{r}
model_DT_up <- train(Class~., data=credit_up, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT_up
prediction_DT_up = predict(model_DT_up, credit_up)
confusionMatrix(prediction_DT_up, credit_up$Class)
```

use SMOTE to improve minority class prediction
```{r}
set.seed(1991)
credit_smote <- SMOTE(class~., data=credit)                         
table(credit_smote$class) 
```

build decision tree model based on SMOTEed data
```{r}
model_DT_smote <- train(class~., data=credit_smote, method='J48', trControl=ctrl_cv10, tuneGrid=expand.grid(C=0.16, M=5))
model_DT_smote
prediction_DT_smote = predict(model_DT_smote, credit_smote)
confusionMatrix(prediction_DT_smote, credit_smote$class)
```


